\thetitle

### 2022-03-31 paper/paper.tex
paragraph about reducing memory usage of DPs

\pagebreak
\ifen \section{Introduction}  \else \section{서론} \fi
\ifen This paper considers the following optimization problem:
\else 본 논문은 다음과 같은 최적화 문제를 고려한다.\fi
%\begin{definition}[Optimal college application portfolio] \label{generalproblemstatement}
\begin{align} \label{headlineproblem}
\begin{split}
\text{maximize}\quad & v(\mathcal{X}) =  \operatorname{E}\Bigl[\max\bigr\{t_0,
\max\{t_j Z_j : j \in \mathcal{X}\}\bigr\}\Bigr] \\
\text{subject to}\quad & \mathcal{X} \subseteq \mathcal{C}, ~~\sum_{j\in \mathcal{X}} g_j \leq H
\end{split}
\end{align}
%\end{definition}
\ifen Here $\mathcal{C} = \{ 1 \dots m\}$ is an index set; $H > 0$ is a budget parameter; for $j = 1 \dots m$, $g_j > 0$ is a cost parameter and $Z_j$ is a random, independent Bernoulli variable with probability $f_j$; and for $j = 0\dots m$, $t_j$ is a utility parameter. 
\else 단,  $\mathcal{C} = \{ 1 \dots m\}$은 지표 집합이며 $H$는 예산을 나타내는 모수이다. 각 $j = 1 \dots m$에 대해 $g_j > 0$는 비용 모수이며 $Z_j$는 확률 $f_j$를 가지는 서로 독립적인 Bernoulli 변수이다. 각 $j = 0 \dots m$에 대해 $t_j$는 효용 모수이다. \fi

@@

\ifen
The college application problem is not solely of theoretical interest. In the American college consulting industry, students pay private consultants an average of \$200 per hour for assistance in preparing application materials, estimating their admissions odds, and identifying target schools (Sklarow 2018). In Korea, an important revenue stream for admissions consulting firms such as Megastudy (\url{megastudy.net}) and Jinhak (\url{jinhak.com}) is ``mock application'' software that claims to use artificial intelligence to optimize the client's application strategy.  Due to the widespread perception that career earnings depend on college admissions outcomes, the solution of \eqref{headlineproblem} holds monetary value. However, although predicting admissions outcomes on a school-by-school basis is a standard benchmark for regression models (Acharya et al. 2019), we believe our study is the first to formulate the overall application strategy as an optimization problem. 
\else
대학 지원 최적화 문제는 이론적인 화제일 뿐만이 아니다. 미국 입학 컨설팅 산업에서 대학 지원 서류 작성, 합격 확률 추정, 그리고 지원 학교를 선택하는 데에 자문하는 개인 상담가의 시간당 비율은 평균 200달러이다 (Sklarow 2018). 한국에서, 메가스터디(\url{megastudy.net})와 진학(\url{jinhak.com})과 같은 입학 컨설팅 기업의 주된 수입원 중 인공지능을 활용해서 학생의 지원 전략을 최대화한다고 홍보하는 ``모의 지원'' 소프트웨어가 있다. 미래의 소득이 대학 입학 결과로 결정된다는 넓은 인식에 따라, \eqref{headlineproblem}의 최적해는 금전적인 가치를 가지고 있다. 그러나, 학교 개별 합격 확률을 추정하는 것은 회귀 분석 모형의 익숙한 응용 사례(Acharya et al. 2019)이지만, 전체적인 지원 전략을 최적화 문제로 모형화한 것은 본 연구의 새로운 기여로 보인다.
\fi

@@

\ifen \subsection{Structure of this paper} \else \subsection{본 논문의 구성}\fi
\ifen Section \ref{preliminaries} introduces some additional notation and assumptions that can be imposed with trivial loss of generality. 
\else \ref{preliminaries}절은 표기법과 일반성을 제한하지 않는 편의적 가정을 제시한다.\fi

\ifen
In section \ref{homogappcosts}, we consider the special case where each $g_j = 1$ and $H$ is an integer $h \leq m$.  We show that an intuitive heuristic is in fact a $1/h$-approximation algorithm. Then, we show that the optimal portfolios are nested in the budget constraint, which yields an exact algorithm that runs in $O(hm)$-time.
\else
\ref{homogappcosts}절에서 각 $g_j = 1$이고 $H$가 $h \leq m$이고 자연수인 특수한 경우를 고려한다. 직관적인 휴리스틱 해법이 실제로 $1/h$-근사 해법임을 증명한다. 그다음에 최적 포트폴리오의 예산 제약에 대한 포함 사슬 관계를 보이고 이를 이용해서 $O(hm)$-시간 정확한 해법을 도출한다.
\fi

\ifen
In section \ref{hetappcosts}, we turn to the scenario in which colleges differ in their application fees. We show that the decision form of the portfolio optimization problem is NP-complete through a polynomial reduction from the binary knapsack problem. We provide three algorithms for this more general setup. The first is a branch-and-bound routine. The second is a dynamic program that iterates on total expenditures and produces an exact solution in pseudopolynomial time, namely $O(Hm + m \log m)$. The third is a different dynamic program that iterates on truncated portfolio valuations. It yields a fully polynomial-time approximation scheme that produces a $(1 - \varepsilon)$-optimal solution in $O(m^3 / \varepsilon)$ time.  
\else
\ref{hetappcosts}절에서 각 학교의 지원 비용이 동일하지 않은 일반적인 상황을 다룬다. 이진 배낭 문제에서의 다항 변환을 통해서 포트폴리오 최적화 문제가 NP-complete임을 증명한다. 또한 3개의 일반적인 해법을 제안한다. 첫째는 분지한계법이다. 둘째는 총 지출액으로 탐색하는 $O(Hm + m \log m)$과 같은 의사 다항 시간 동적 계획 해법이다. 셋째는 실수값을 분수값으로 내림한 포트폴리오 가치를 탐색하는 또다른 동적 계획 해법이다. 이를 통해서 $O(m^3 / \varepsilon)$-시간 안에 $(1 - \varepsilon)$-근사해를 출력하는 완전 다항 시간 근사 해법(fully polynomial-time approximation scheme)을 얻는다.
\fi

\ifen
In section \ref{numericalexperiments}, we present the results of computational experiments that confirm the validity and time complexity results established in the previous two sections.

@@

\begin{theorem}[\ifen Accuracy of the na\"ive algorithm\else 나이브 해법의 정확성\fi] \label{oneoverhopt}
\ifen 
When the application limit is $h$, let $\mathcal{X}_h$ denote the optimal portfolio, and $\mathcal{T}_h$ the set of the $h$ schools having the largest values of $f_j t_j$. Then $v(\mathcal{T}_h) / v(\mathcal{X}_h) \geq 1/h$. 
\else
지원 제한이 $h$일 때, 최적 포트폴리오가 $\mathcal{X}_h$이고 기대 효용 $f_j t_j$가 가장 높은 $h$개의 학교의 집합이 $\mathcal{T}_h$라고 하자. 그러면 $v(\mathcal{T}_h) / v(\mathcal{X}_h) \geq 1/h$이다.
\fi
\end{theorem}
\begin{proof}
\ifen
Because $\mathcal{T}_h$ maximizes the quantity $\operatorname{E}\bigl[ \sum_{j \in \mathcal{T}_h}\{ t_j Z_j \}\bigr]$, we have
\else
$\mathcal{T}_h$는 $\operatorname{E}\bigl[ \sum_{j \in \mathcal{T}_h}\{ t_j Z_j \}\bigr]$를 최대화하므로,
\fi
\begin{align} \label{oneoverhopt}
\begin{split}
v(\mathcal{X}_h) &= \operatorname{E}\bigl[ \max_{j \in \mathcal{X}_h}\{ t_j Z_j \}\bigr] \leq \operatorname{E}\bigl[ \sum_{j \in \mathcal{X}_h}\{ t_j Z_j \}\bigr] \leq \operatorname{E}\bigl[ \sum_{j \in \mathcal{T}_h}\{ t_j Z_j \}\bigr] \\
&= h  \operatorname{E}\bigl[ \tfrac{1}{h} \sum_{j \in \mathcal{T}_h}\{ t_j Z_j \}\bigr]
\leq h  \operatorname{E}\bigl[ \max_{j \in \mathcal{T}_h}\{ t_j Z_j \}\bigr]
= h\,v(\mathcal{T}_h).
\end{split}
\end{align}
\ifen 
where the final inequality follows from the concavity of the $\max\{\}$ operator.
\else
단, 마지막 부등호는 $\max\{\}$ 연산의 볼록성에 따라 성립한다.
\fi
\end{proof}

@@

\begin{proof}\ifen
By induction on $h$. Applying Theorem \ref{assumetzerozero}, we assume that $t_0 = 0$.

(Base case.) First, we will show that $\mathcal{X}_1 \subset \mathcal{X}_2$. To get a contradiction, suppose that the optima are $\mathcal{X}_1 = \{j\}$ and $\mathcal{X}_2 = \{k, l\}$, where we may assume that $t_k \leq t_l$. Optimality requires that
\else$h$에 대해 귀납법을 적용한다. 정리 \ref{assumetzerozero}에 따라 $t_0 = 0$이라고 가정한다.

@@

\ifen 
It is also possible to store $\mathcal{C}$ as a binary max heap rather than a list. The heap is ordered according to the criterion $i \geq j \iff f_i t_i \geq f_j t_j$, and by draining the heap and reheapifying at the end of each iteration, the computation time remains $O(hm)$. However, in our numerical experiments, whose results are reported in section \ref{numericalexperiments},
we found the list implementation to be much faster, because it is possible to identify the entering school $k$ as the utility parameters are updated, which all but eliminates the cost of the $\argmax\{\}$ operation. 
\else
$\mathcal{C}$는 목록 대신 이진 최대 힙 구현으로 저장하는 방법도 고려한다. 단, 힙의 순서는 $i \geq j \iff f_i t_i \geq f_j t_j$의 조건으로 정의하며, 각 반복단계의 마지막 단계에서 힙을 비우고 다시 힙화(heapify)하면 $O(hm)$ 계산 시간을 유지할 수 있다. 그러나 (\ref{numericalexperiments}절에서 결과를 제시할) 수리 실험에서 목록 구현으로 구성한 알고리즘이 더 빨랐다. 효용 모수를 수정하면서 $k$를 구함으로 $\argmax\{\}$ 연산의 계산 비용을 거의 제거할 수 있기 때문이다.
\fi

@@

\ifen \subsection{NP-completeness} \else \subsection{NP-completeness}\fi
\ifen
The optima for Ellis's problem are not necessarily nested, nor is the number of schools in the optimal portfolio necessarily increasing in $H$. For example, if
$f = (0.5, 0.5, 0.5)$, $t = (1, 1, 219)$, and $g = (1, 1, 3)$,
then it is evident that the optimal portfolio for $H = 2$ is $\{1, 2\}$ while that for $H = 3$ is $\{3\}$. In fact, Ellis’s problem is NP-complete, as we will show by a transformation from the binary knapsack problem, which is known to be NP-complete (Garey and Johnson 1979).
\else
엘리스 문제의 최적해는 필수적으로 포함 사슬 관계를 가지지 않으며 최적 포트폴리오에 속한 학교의 개수는 $H$에 대해 감소할 수도 있다. 예를 들어
$f = (0.5, 0.5, 0.5)$, $t = (1, 1, 219)$, 그리고 $g = (1, 1, 3)$이면 $H = 2$에 대응하는 최적해가 $\{1, 2\}$이며 $H = 3$에 대응하는 최적해는 $\{3\}$임을 쉽게 알 수 있다. 사실은 엘리스의 문제가 NP-complete이며 이를 이진 배낭 문제에서의 변환을 통해 증명할 수 있다. 배낭 문제의 NP-completeness가 이미 알려져 있다 (Garey and Johnson 1979).
\fi

@@

\ifen
To begin, let us characterize the portfolio $\mathcal{X}$ as the binary vector $x \in \{0, 1\}^m$, where $x_j = 1 $ if and only if $j \in \mathcal\{X\}$. Then it is not difficult to see that Ellis's problem is equivalent to the following integer nonlinear program. 
\else
우선 포트폴리오 $\mathcal{X}$를 이진 특성 벡터 $x \in \{0, 1\}^m$로 표현하자. 단, $x_j = 1 $인 것은 $j \in \mathcal\{X\}$과 동치다. 그러면 엘리스의 문제가 다음 비선형 정수 최적화 문제와 동등함을 볼 수 있다.
\fi
\begin{problem}[\ifen Integer NLP for Ellis's problem\else 엘리스의 문제를 위한 비선형 정수 계획\fi] \label{integernlp}
\begin{align}
\begin{split}
\text{maximize}\quad &  v(x) = \sum_{j=1}^m \Bigl(f_j t_j  x_j \prod_{i > j} (1 - f_{i} x_i) \Bigr)\\
\text{subject to}\quad & \sum_{j=1}^m g_j x_j \leq H, ~~ x_i \in \{0, 1\}^m
\end{split}
\end{align}
\end{problem}
\ifen
Since the product in $v(x)$ does not exceed one, the following LP relaxation is an upper bound on the valuation of the optimal portfolio.
\else
$v(x)$에서 등장하는 곱은 1을 넘을 수 없으므로 다음 선형 완화 문제는 최적 포트폴리오 가치의 상한이 된다.
\fi
\begin{problem}[\ifen LP relaxation for Ellis's problem\else 엘리스의 문제를 위한 선형 완화 문제\fi] \label{LPrelaxation}
\begin{align}
\begin{split}
\text{maximize}\quad &  v_{\mathrm{LP}}(x) = \sum_{j=1}^m  f_j t_j x_j \\
\text{subject to}\quad & \sum_{j=1}^m g_j x_j \leq H, ~~ x \in [0, 1]^m
\end{split}
\end{align}
\end{problem}
\ifen
Problem \ref{LPrelaxation} is a continuous knapsack problem, which is easily solved in $O(m \log m)$-time by the following greedy algorithm: Start with $x = \mathbf{0}$. While $H > 0$, select the school $j$ for which $f_j t_j / g_j$ is highest, set $x_j \gets \min\{1, H / g_j\}$, and set $H \gets H - g_j$ (Dantzig 1957).  
\else
문제 \ref{LPrelaxation}은(는) ``연속 배낭 문제''라고 불리며 다음 탐욕 알고리즘을 적용하면 $O(m \log m)$-시간 안에 쉽게 풀 수 있다: $x = \mathbf{0}$로 초기화한다. $H > 0$임이 성립하는 동안, $f_j t_j / g_j$-값이 가장 높은 학교 $j$를 택한다. $x_j \gets \min\{1, H / g_j\}$ 그리고 $H \gets H - g_j$로 수정해서 반복한다 (Dantzig 1957).
\fi

>>>>

\pagebreak
\ifen \section{Introduction}  \else \section{서론} \fi
\ifen This paper considers the following optimization problem:
\else 본 논문은 다음과 같은 최적화 문제를 고려한다.\fi
%\begin{definition}[Optimal college application portfolio] \label{generalproblemstatement}
\begin{align} \label{headlineproblem}
\begin{split}
\text{maximize}\quad & v(\mathcal{X}) =  \operatorname{E}\Bigl[\max\bigr\{t_0,
\max\{t_j Z_j : j \in \mathcal{X}\}\bigr\}\Bigr] \\
\text{subject to}\quad & \mathcal{X} \subseteq \mathcal{C}, ~~\sum_{j\in \mathcal{X}} g_j \leq H
\end{split}
\end{align}
%\end{definition}
\ifen Here $\mathcal{C} = \{ 1 \dots m\}$ is an index set; $H > 0$ is a budget parameter; for $j = 1 \dots m$, $g_j > 0$ is a cost parameter and $Z_j$ is a random, independent Bernoulli variable with probability $f_j$; and for $j = 0\dots m$, $t_j\geq 0$ is a utility parameter. 
\else 단,  $\mathcal{C} = \{ 1 \dots m\}$은 지표 집합이며 $H$는 예산을 나타내는 모수이다. 각 $j = 1 \dots m$에 대해 $g_j > 0$는 비용 모수이며 $Z_j$는 확률 $f_j$를 가지는 서로 독립적인 Bernoulli 변수이다. 각 $j = 0 \dots m$에 대해 $t_j\geq 0$는 효용 모수이다. \fi

@@

\ifen
The college application problem is not solely of theoretical interest. In the American college consulting industry, students pay private consultants an average of \$200 per hour for assistance in preparing application materials, estimating their admissions odds, and identifying target schools (Sklarow 2018). In Korea, an important revenue stream for admissions consulting firms such as Megastudy (\url{megastudy.net}) and Jinhak (\url{jinhak.com}) is ``mock application'' software that claims to use artificial intelligence to optimize the client's application strategy.  Due to the widespread perception that career earnings depend on college admissions outcomes, the solution of \eqref{headlineproblem} holds monetary value. However, although predicting admissions outcomes on a school-by-school basis is a standard benchmark for regression models (Acharya et al. 2019), we believe our study is the first to formulate the overall application strategy as an optimization problem. 
\else
대학 지원 최적화 문제는 이론적인 화제일 뿐만이 아니다. 미국 입학 컨설팅 산업에서 대학 지원 서류 작성, 합격 확률 추정, 그리고 지원 학교를 선택하는 데에 자문하는 개인 상담가의 시간당 급료는 평균 200달러이다 (Sklarow 2018). 한국에서, 메가스터디(\url{megastudy.net})와 진학(\url{jinhak.com})과 같은 입학 컨설팅 기업의 주된 수입원 중 인공지능을 활용해서 학생의 지원 전략을 최대화한다고 홍보하는 ``모의 지원'' 소프트웨어가 있다. 미래의 소득이 대학 입학 결과로 결정된다는 넓은 인식에 따라, \eqref{headlineproblem}의 최적해는 금전적인 가치를 가지고 있다. 그러나, 학교 개별 합격 확률을 추정하는 것은 회귀 분석 모형의 익숙한 응용 사례(Acharya et al. 2019)이지만, 전체적인 지원 전략을 최적화 문제로 모형화한 것은 본 연구의 새로운 기여로 보인다.
\fi

@@

\ifen \subsection{Structure of this paper} \else \subsection{본 논문의 구성}\fi
\ifen Section \ref{preliminaries} introduces some additional notation and assumptions that can be imposed without loss of generality. 
\else \ref{preliminaries}절은 표기법과 일반성을 제한하지 않는 편의적 가정을 제시한다.\fi

\ifen
In Section \ref{homogappcosts}, we consider the special case where each $g_j = 1$ and $H$ is an integer $h \leq m$.  We show that an intuitive heuristic is in fact a $1/h$-approximation algorithm. Then, we show that the optimal portfolios are nested in the budget constraint, which yields an exact algorithm that runs in $O(hm)$-time.
\else
\ref{homogappcosts}절에서 각 $g_j = 1$이고 $H$가 $h \leq m$이고 자연수인 특수한 경우를 고려한다. 직관적인 휴리스틱 해법이 실제로 $1/h$-근사 해법임을 증명한다. 그다음에 최적 포트폴리오의 예산 제약에 대한 포함 사슬 관계를 보이고 이를 이용해서 $O(hm)$-시간 정확한 해법을 도출한다.
\fi

\ifen
In Section \ref{hetappcosts}, we turn to the scenario in which colleges differ in their application fees. We show that the decision form of the portfolio optimization problem is NP-complete through a polynomial reduction from the binary knapsack problem. We provide three algorithms for this more general setup. The first is a branch-and-bound routine. The second is a dynamic program that iterates on total expenditures and produces an exact solution in pseudopolynomial time, namely $O(Hm + m \log m)$. The third is a different dynamic program that iterates on truncated portfolio valuations. It yields a fully polynomial-time approximation scheme that produces a $(1 - \varepsilon)$-optimal solution in $O(m^3 / \varepsilon)$ time.  
\else
\ref{hetappcosts}절에서 각 학교의 지원 비용이 동일하지 않은 일반적인 상황을 다룬다. 이진 배낭 문제에서의 다항 변환을 통해서 포트폴리오 최적화 문제가 NP-complete임을 증명한다. 또한 3개의 일반적인 해법을 제안한다. 첫째는 분지한계법이다. 둘째는 총 지출액으로 탐색하는 $O(Hm + m \log m)$과 같은 의사 다항 시간 동적 계획 해법이다. 셋째는 실수값을 분수값으로 내림한 포트폴리오 가치를 탐색하는 또다른 동적 계획 해법이다. 이를 통해서 $O(m^3 / \varepsilon)$-시간 안에 $(1 - \varepsilon)$-근사해를 출력하는 완전 다항 시간 근사 해법(fully polynomial-time approximation scheme)을 얻는다.
\fi

\ifen
In Section \ref{numericalexperiments}, we present the results of computational experiments that confirm the validity and time complexity results established in the previous two sections.

@@

\begin{theorem}[\ifen Accuracy of the na\"ive algorithm\else 나이브 해법의 정확성\fi] \label{oneoverhopt}
\ifen 
When the application limit is $h$, let $\mathcal{X}_h$ denote the optimal portfolio, and $\mathcal{T}_h$ the set of the $h$ schools having the largest values of $f_j t_j$. Then $v(\mathcal{T}_h) / v(\mathcal{X}_h) \geq 1/h$. 
\else
지원 제한이 $h$일 때, 최적 포트폴리오가 $\mathcal{X}_h$이고 기대 효용 $f_j t_j$가 가장 높은 $h$개의 학교의 집합이 $\mathcal{T}_h$라고 하자. 그러면 $v(\mathcal{T}_h) / v(\mathcal{X}_h) \geq 1/h$이다.
\fi
\end{theorem}
\begin{proof}
\ifen
Because $\mathcal{T}_h$ maximizes the quantity $\operatorname{E}\bigl[ \sum_{j \in \mathcal{T}_h}\{ t_j Z_j \}\bigr]$, we have
\else
$\mathcal{T}_h$는 $\operatorname{E}\bigl[ \sum_{j \in \mathcal{T}_h}\{ t_j Z_j \}\bigr]$를 최대화하므로,
\fi
\begin{align} \label{oneoverhopt}
\begin{split}
v(\mathcal{X}_h) &= \operatorname{E}\Bigl[ \max_{j \in \mathcal{X}_h}\{ t_j Z_j \}\Bigr] \leq \operatorname{E}\Bigl[ \sum_{j \in \mathcal{X}_h}\{ t_j Z_j \}\Bigr] \leq \operatorname{E}\Bigl[ \sum_{j \in \mathcal{T}_h}\{ t_j Z_j \}\Bigr] \\
&= h  \operatorname{E}\Bigl[ \tfrac{1}{h} \sum_{j \in \mathcal{T}_h}\{ t_j Z_j \}\Bigr]
\leq h  \operatorname{E}\Bigl[ \max_{j \in \mathcal{T}_h}\{ t_j Z_j \}\Bigr]
= h v(\mathcal{T}_h).
\end{split}
\end{align}
\ifen 
where the final inequality follows from the concavity of the $\max\{\}$ operator.
\else
단, 마지막 부등호는 $\max\{\}$ 연산의 볼록성에 따라 성립한다.
\fi
\end{proof}

@@

\begin{proof}\ifen
By induction on $h$. Applying Theorem \ref{assumetzerozero}, we assume that $t_0 = 0$. We also assume that each $f_j < 1$, which is without loss of generality because any school having $f_j = 1$ can be eliminated by setting $t_0 = t_j$ and reapplying the transformation from Theorem \ref{assumetzerozero}.

(Base case.) First, we will show that $\mathcal{X}_1 \subset \mathcal{X}_2$. To get a contradiction, suppose that the optima are $\mathcal{X}_1 = \{j\}$ and $\mathcal{X}_2 = \{k, l\}$, where we may assume that $t_k \leq t_l$. Optimality requires that
\else$h$에 대해 귀납법을 적용한다. 정리 \ref{assumetzerozero}에 따라 $t_0 = 0$이라고 가정한다. 또한 모든 $f_j < 1$임을 가정한다. $f_j = 1$인 학교가 있으면 $t_0 = t_j$로 수정하고  정리 \ref{assumetzerozero}의 변환을 다시 적용해서 소거할 수 있으므로 일반성을 제한하지 않는다.

@@

\ifen 
It is also possible to store $\mathcal{C}$ as a binary max heap rather than a list. The heap is ordered according to the criterion $i \geq j \iff f_i t_i \geq f_j t_j$, and by draining the heap and reheapifying at the end of each iteration, the computation time remains $O(hm)$. However, in our numerical experiments, whose results are reported in Section \ref{numericalexperiments},
we found the list implementation to be much faster, because it is possible to identify the entering school $k$ as the utility parameters are updated, which all but eliminates the cost of the $\argmax\{\}$ operation. 
\else
$\mathcal{C}$는 목록 대신 이진 최대 힙 구현으로 저장하는 방법도 고려한다. 단, 힙의 순서는 $i \geq j \iff f_i t_i \geq f_j t_j$의 조건으로 정의하며, 각 반복단계의 마지막 단계에서 힙을 비우고 다시 힙화(heapify)하면 $O(hm)$ 계산 시간을 유지할 수 있다. 그러나 (\ref{numericalexperiments}절에서 결과를 제시할) 수리 실험에서 목록 구현으로 구성한 알고리즘이 더 빨랐다. 효용 모수를 수정하면서 $k$를 구함으로 $\argmax\{\}$ 연산의 계산 비용을 거의 제거할 수 있기 때문이다.
\fi

@@

\ifen \subsection{NP-completeness} \else \subsection{NP-completeness}\fi
\ifen
The optima for Ellis's problem are not necessarily nested, nor is the number of schools in the optimal portfolio necessarily increasing in $H$. For example, if
$f = (0.5, 0.5, 0.5)$, $t = (1, 1, 219)$, and $g = (1, 1, 3)$,
then it is evident that the optimal portfolio for $H = 2$ is $\{1, 2\}$ while that for $H = 3$ is $\{3\}$. In fact, Ellis’s problem is NP-complete, as we will show by a transformation from the binary knapsack problem, which is known to be NP-complete (Garey and Johnson 1979, \S\,3.2.1).
\else
엘리스 문제의 최적해는 필수적으로 포함 사슬 관계를 가지지 않으며 최적 포트폴리오에 속한 학교의 개수는 $H$에 대해 감소할 수도 있다. 예를 들어
$f = (0.5, 0.5, 0.5)$, $t = (1, 1, 219)$, 그리고 $g = (1, 1, 3)$이면 $H = 2$에 대응하는 최적해가 $\{1, 2\}$이며 $H = 3$에 대응하는 최적해는 $\{3\}$임을 쉽게 알 수 있다. 사실은 엘리스의 문제가 NP-complete이며 이를 이진 배낭 문제에서의 변환을 통해 증명할 수 있다. 배낭 문제의 NP-completeness가 이미 알려져 있다 (Garey and Johnson 1979, \S\,3.2.1).
\fi

@@

\ifen
To begin, let us characterize the portfolio $\mathcal{X}$ as the binary vector $x \in \{0, 1\}^m$, where $x_j = 1 $ if and only if $j \in \mathcal\{X\}$. Then it is not difficult to see that Ellis's problem is equivalent to the following integer nonlinear program. 
\else
우선 포트폴리오 $\mathcal{X}$를 이진 특성 벡터 $x \in \{0, 1\}^m$로 표현하자. 단, $x_j = 1 $인 것은 $j \in \mathcal\{X\}$과 동치다. 그러면 엘리스의 문제가 다음 비선형 정수 최적화 문제와 동등함을 볼 수 있다.
\fi
\begin{problem}[\ifen Integer NLP for Ellis's problem\else 엘리스의 문제를 위한 비선형 정수 계획\fi] \label{integernlp}
\begin{align}
\begin{split}
\text{maximize}\quad &  v(x) = \sum_{j=1}^m \Bigl(f_j t_j  x_j \prod_{i > j} (1 - f_{i} x_i) \Bigr)\\
\text{subject to}\quad & \sum_{j=1}^m g_j x_j \leq H, ~~ x_i \in \{0, 1\}^m
\end{split}
\end{align}
\end{problem}
\ifen
Since the product in $v(x)$ does not exceed one, the following LP relaxation is an upper bound on the valuation of the optimal portfolio.
\else
$v(x)$에서 등장하는 곱은 1을 넘을 수 없으므로 다음 선형 완화 문제는 최적 포트폴리오 가치의 상한이 된다.
\fi
\begin{problem}[\ifen LP relaxation for Ellis's problem\else 엘리스의 문제를 위한 선형 완화 문제\fi] \label{LPrelaxation}
\begin{align}
\begin{split}
\text{maximize}\quad &  v_{\mathrm{LP}}(x) = \sum_{j=1}^m  f_j t_j x_j \\
\text{subject to}\quad & \sum_{j=1}^m g_j x_j \leq H, ~~ x \in [0, 1]^m
\end{split}
\end{align}
\end{problem}
\ifen
Problem \ref{LPrelaxation} is a continuous knapsack problem, which is easily solved in $O(m \log m)$-time by the following greedy algorithm: Start with $x = \mathbf{0}$. While $H > 0$, select the school $j$ for which $f_j t_j / g_j$ is highest, set $x_j \gets \min\{1, H / g_j\}$, and set $H \gets H - g_j$ (Dantzig 1957). Balas and Zemel (1980, \S\,2) provide an $O(m)$ algorithm. 
\else
문제 \ref{LPrelaxation}은(는) ``연속 배낭 문제''라고 불리며 다음 탐욕 알고리즘을 적용하면 $O(m \log m)$-시간 안에 쉽게 풀 수 있다: $x = \mathbf{0}$로 초기화한다. $H > 0$임이 성립하는 동안, $f_j t_j / g_j$-값이 가장 높은 학교 $j$를 택한다. $x_j \gets \min\{1, H / g_j\}$ 그리고 $H \gets H - g_j$로 수정해서 반복한다 (Dantzig 1957).  $O(m)$ 알고리즘도 알려져 있다 (Balas와 Zemel 1980, \S\,2).
\fi

\ifen 
In our branch-and-bound framework, a \emph{node} is characterized by a three-way partition of schools $\mathcal{C}= \mathcal{I} \cup \mathcal{O} \cup \mathcal{N}$ satisfying $\sum_{j \in \mathcal{I}} g_j \leq H$. $\mathcal{I}$ consists of schools that are ``in'' the application portfolio ($x_j = 1$), $\mathcal{O}$ consists of those that are ``out'' ($x_j = 0$), and $\mathcal{N}$ consists of those that are ``negotiable.'' 
%This partition induces a constant $\gamma$, transformed $t_j$-values $\bar t$, the residual budget $\mathcal{H}$, and a set $\mathcal{L}$ of pointers to the node's children, if any.
The choice of partition induces a pair of subproblems. The first subproblem is an instance of Problem \ref{integernlp}, namely
\else
본 연구의 분지한계법 설계에서, `마디'(node)는 학교를 세 군으로 나눈 분할 $\mathcal{C}= \mathcal{I} \cup \mathcal{O} \cup \mathcal{N}$로 묘사한다. 단, $\mathcal{I}$는 $\sum_{j \in \mathcal{I}} g_j \leq H$을 만족한다. $\mathcal{I}$는 지원 포트폴리오에 속한 학교(`in': $x_j = 1$), $\mathcal{O}$는 속하지 않은 학교(`out': $x_j = 0$), 그리고 $\mathcal{N}$은 미결의 학교(`negotiable')로 이루어진다. 분할이 결정되면 부문제의 한 쌍이 결정해진다. 첫번째 부문제는 다음 같은 문제 \ref{integernlp}의 인스턴스다.
\fi
\begin{align} \label{nodenlpsubproblem}
\begin{split}
\text{maximize}\quad &  v(x) = \gamma + \sum_{j \in \mathcal{N}} \Bigl(f_j \bar t_j x_j \prod_{\substack{i \in \mathcal{N}:\\i > j}} (1 - f_{i} x_i) \Bigr)\\
\text{subject to}\quad & \sum_{j \in \mathcal{N}} g_j x_j \leq \bar H; ~~ x_j \in \{0, 1\},~~j \in \mathcal{N}.
\end{split}
\end{align}
\ifen The second is the corresponding instance of Problem \ref{LPrelaxation}:
\else 두번째 부문제는 대응하는 문제 \ref{LPrelaxation} 인스턴스다.\fi
\begin{align} \label{nodelprelaxation}
\begin{split}
\text{maximize}\quad &  w_{\mathrm{LP}}(x)= \gamma + \sum_{j \in \mathcal{N}}  f_j \bar t_j  x_j \\
\text{subject to}\quad & \sum_{j \in \mathcal{N}} g_j x_j \leq \bar H; ~~ x_j \in [0, 1],~~j \in \mathcal{N}
\end{split}
\end{align}
\ifen
In both subproblems, $\bar H = H - \sum_{j\in \mathcal{I}} g_j$ denotes the residual budget. The parameters $\gamma$ and $\bar t$ are obtained by iteratively applying the transformation \eqref{howtotransformfj} to the schools in $\mathcal{I}$. For each $j\in \mathcal{I}$,  we increment $\gamma$ by the current value of $f_j \bar t_j$, eliminate $j$ from the market, and update the remaining $\bar t_j$-values using \eqref{howtotransformfj}. (An example is given below.)
\else
각 부문제에서 $\bar H = H - \sum_{j\in \mathcal{I}} g_j$는 잔여 예산을 의미한다. $\mathcal{I}$에 속한 학교에 \eqref{howtotransformfj}의 변환을 적용해서 모수 $\gamma$와 $\bar t$를 얻을 수 있다. 즉, 각 $j\in \mathcal{I}$에 대해 $\gamma$를 $f_j \bar t_j$ 만큼 증가시키고, 시장에서 $j$를 소거하고, \eqref{howtotransformfj}에 따라 남은 $\bar t_j$-값을 수정한다. (아래에서 예를 제시한다.)
\fi
